Early Observations of the Type Ia Supernova \abc:\\ Evidence for Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-08-17 doc/ms.tex
Update caption for the companion-interaction figure

\begin{figure}[!thb]
  \centering
  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
  \caption{Comparison of SN ejecta-companion interaction models 
  with early observations of \abc. $g_\mathrm{PTF}$ observations 
  (green) detections and 3$\sigma$ upper limits are shown 
  as circles and downward arrows, respectively. The initial 
  \textit{Swift}/$UVW1$ observation (magenta) is shown as a 
  hexagon.
  The dashed, solid, and dash-dot lines show the expected flux 
  for various companion interaction models in 
  the $g_\mathrm{PTF}$ (green) and $UVW1$ (magenta) filters. The 
  models have been adjusted to account for the distance and 
  reddening towards \abc. Each 
  model features a different companion semi-major axis, $a$, and 
  time of explosion, $t_\mathrm{exp}$, as labeled in the 
  legend. While models with $a \gtrsim 10^{13} \, \mathrm{cm}$ can 
  explain the early $g_\mathrm{PTF}$ emission, they greatly 
  overpredict the flux in the UV. If the time of explosion is 
  $\sim$1 d prior to $t_0$, then models with $a \approx 10^{12} \, 
  \mathrm{cm}$ can explain the initial detection \abc, but they 
  fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
  explosion.
  }
  \label{fig:SN-companion}
\end{figure}

>>>>

\begin{figure}[!thb]
  \centering
  \includegraphics[width=0.48\textwidth]{companion_lc.pdf}
  \caption{Comparison of SN ejecta-companion interaction models 
  with early observations of \abc. $g_\mathrm{PTF}$ observations 
  (green) detections and 3$\sigma$ upper limits are shown 
  as circles and downward arrows, respectively. 
  \textit{Swift}/$UVW1$ observations (magenta) are shown as hexagons.
  The dashed, solid, and dash-dot lines show the expected flux 
  for companion interaction models in the $g_\mathrm{PTF}$ (green) 
  and $UVW1$ (magenta) filters. The models have been adjusted to 
  account for the distance and reddening towards \abc. Each 
  model features a different companion semi-major axis, $a$, and 
  time of explosion, $t_\mathrm{exp}$, as labeled in the 
  legend. While models with $a \gtrsim 10^{12} \, \mathrm{cm}$ can 
  explain the early rise in $g_\mathrm{PTF}$, they greatly 
  overpredict the flux in the UV. Models with $a \approx 10^{11} \, 
  \mathrm{cm}$ can explain the initial detection \abc, but they 
  fail to replicate the $\sim$2 mag rise in the $\sim$24 hr after 
  explosion.
  }
  \label{fig:SN-companion}
\end{figure}
